Evaluation of a Cache-Oblivious Data Structure [draft-1]

### 2008-05-31 paper/paper.tex
Updated paper abstract. Updated plot labels.

\title{Evaluation of Cache-Oblivious Data Structures [draft-1]}

@@

\begin{abstract}
In modern computer hardware architecture memory is organized in a hierarchy
consisting of several types of memory with different memory sizes, block
transfer sizes and access times. To reflect this situation more accurately
than traditional models, the cache-oblivious model has been proposed, and
several algorithms and data structures have been developed that perform
optimally in this model.
This paper presents the results of an empirical evaluation of several data
structures in a realistic scenario, and gives insight into the applicability
of cache-oblivious data structure in practice.
\end{abstract}

@@

Finally, in Figure \ref{fig-eratosthenes-bender_wctime} the execution times for
the Bender set with several different density parameters are given. With a lower
density, more space is required, but new insertions less frequently cause large windows to be rebalanced.
Suprisingly, the execution times for the different density values are comparable.
Figure \ref{fig-eratosthenes-bender_vss} shows that the lower density parameters do
indeed use a lot more memory. It appears that the advantage of low density is
negated by the overhead of constructing increasingly large data structures.
The set with $\delta=0.125$ cannot even finish the test case in the memory
that is available. Since execution times are similar, we select
$\delta=0.5$ for future experiments in order to minimize memory use.

@@

\bibliographystyle{plain}
\bibliography{paper}

>>>>

\title{Evaluation of a Cache-Oblivious Data Structure [draft-1]}

@@

\begin{abstract}
In modern computer hardware architecture memory is organized in a hierarchy
consisting of several types of memory with different memory sizes, block
transfer sizes and access times.
Traditionally, data structures are evaluated in a theoretical model that
does not take the existance of a memory hierarchy into account. The
cache-oblivious model has been proposed as a more accurate model.
Although several data structures have been described in this model
relatively little empirical performance data is available.
This paper presents the results of an empirical evaluation of several data
structures in a realistic scenario and aims to provide insight into
the applicability of cache-oblivious data structures in practice.
\end{abstract}

@@

Finally, in Figure \ref{fig-eratosthenes-bender_wctime} the execution times for
the Bender set with several different density parameters are given. With a lower
density, more space is required, but new insertions less frequently cause large windows to be rebalanced.
The execution times for the density values of 0.5 and lower are almost the same
while larger density values are slower.
Figure \ref{fig-eratosthenes-bender_vss} shows that the lower the density value,
the more memory is used. It appears that the advantage of low density is
negated by the overhead of constructing increasingly large data structures.
The set with $\delta=0.125$ cannot even finish the test case in the memory
that is available. We select $\delta=0.5$ for future experiments, which strikes
a good balance between execution time and required memory.

@@

\bibliographystyle{unsrt}
\bibliography{paper}
